---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# etherscanr

The package offers an easy way to use the [etherscan.io API](https://etherscan.io/apis) to query information about the Ethereum network. The package uses `Rmpfr` for number represenstation where possible.

Currently work in progress. This is an unofficial package. As always use it at your own risk.


## API

* Accounts
    * `etherscan_transactions` get all transaction of an account
    * `etherscan_balance` retrieve account balances
  
* Stats
    * `etherscan_ethsupply` returns the total Ether supply in Wei
    * `etherscan_lastprice` returns the last price in USD
  
* Helpers
    * `to_ether` converts wei to ether using the Multiple Precision Floating-Point Reliable (MPFR) library.
  

## Example

For example let us examine all the transactions of account [0x6F46CF5569AEfA1acC1009290c8E043747172d89](https://etherscan.io/address/0x6F46CF5569AEfA1acC1009290c8E043747172d89):

```{r example, message=FALSE}
library(etherscanr)
library(dplyr)
library(ggplot2)
etherscan_transactions("0x6F46CF5569AEfA1acC1009290c8E043747172d89") %>% 
  mutate(value = to_ether(value, from = "wei")) %>% 
  filter(value > 0) %>% 
  ggplot(aes(x = timeStamp, y = value)) + 
  geom_point() + 
  stat_smooth() + # we smooth it just be cause it looks nice ;)
  theme(legend.position = "bottom") + 
  expand_limits(y = 0)
```
